\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{a4wide}
\usepackage{geometry}
\usepackage{amsmath}
\usepackage{ellipsis}
\usepackage[pdfborder={0 0 0}]{hyperref}
\geometry{vmargin=2.5cm,hmargin=2cm}
\author{Marvin Cohrs}
\title{Fu Bar}

\begin{document}

	\maketitle
	\tableofcontents
	
	\section{Skills}
	\subsection{Operators + Functions}
	
	Fu Bar knows several operators and functions:
	
	\begin{itemize}
		\item Addition: $x + y$\\
			  Adds two floating-point numbers.\\
			  e.g. $4.1 + 5.8 = 9.9$
		\item Subtraction: $x - y$\\
			  Subtracts a floating-point number from another one.\\
			  e.g. $9.9 - 5.8 = 4.1$
		\item Multiplication: $x * y$\\
			  Multiplies two floating-point numbers.\\
			  e.g. $1.1 * 9.0 = 1.1 \times 9.0 = 9.9$
		\item Division: $x / y$\\
			  Divides a floating-point number by another one.\\
			  e.g. $9.9 / 1.1 = \frac{9.9}{1.1} = 9.0$
		\item Integer division: $n \backslash m$\\
			  Divides an integer by another one and returns the integer quotient.\\
			  e.g. $20 \backslash 6 = 3$\\
			  because $6\times3=18$ and $6\times4=21$
		\item Modulo: $n \# m$\\
			  Divides an integer by another one and returns the modulo.\\
			  e.g. $20 \# 6 = 2$\\
			  because $6\times3+2=20$
		\item Exponentiation: $x \; \hat{ } \; n$\\
			  Exponentiates a floating-point base by an integer exponent.\\
			  e.g. $2 \; \hat{ } \; 8 = 2 ^{8} = 256$
		\item Paranthenses: $(expression)$\\
			  An expression in paranthenses has got a higher priority.\\
			  e.g. $2 * (4 + 5) = 2 * 9 = 18$\\
			  but $2 * 4 + 5 = 8 + 5 = 13$
		\item Absolute Value: $|expression|$, $abs(expression)$\\
			  Gets the absolute value of an expression.\\
			  e.g. $|+3| = 3$\\
			  and $|-3| = 3$, too!
		\item Negation: $-x$, $neg(x)$\\
		      Negates a floating-point number.\\
		      e.g. $- (3 * 2) = -6$
		\item Reciprocal: $1/x$, $rec(x)$\\
			  Divides $\frac{1}{x}$, resulting the reciprocal.\\
			  e.g. $rec(4) = \frac{1}{4} = 0.25$
		\item Factorial: $n!$, $fac(n)$\\
			  Computes the factorial of an integer.\\
			  e.g. $4! = 24$
		\item Binomial Coefficient: $k$ from $n$, $n$C$k$\\
			  Computes the binomial coefficient for $n \choose k$\\
			  e.g. $2$ from $3 = 3$C$2 = {3 \choose 2} = 3$
		\item Square root: $sqrt(x)$, $SquareRoot(x)$\\
			  Computes the square root of a floating-point number.\\
			  e.g. $sqrt(9) = \sqrt{9} = 3$
		\item Cube root: $cbrt(x)$, $CubeRoot(x)$\\
			  Computes the cube root of a floating-point number.\\
			  e.g. $cbrt(27) = \sqrt[3]{27} = 3$
		\item $n$th root: $nrt(x; n)$, $Root(x; n)$\\
			  Computes the $n$th root of a floating-point number.\\
			  e.g. $nrt(4096; 6) = \sqrt[6]{4096} = 4$
		\item Integer reduction: $int(x)$, $x\backslash1$\\
			  Reduces a floating-point number to an integer:\\
			  e.g. $int(tau) = 6$
		\item Cut: $frac(x)$\\
			  Cut's the number at the floating-point, resulting fraction part.\\
			  e.g. $frac(23.45) = 0.45$
		\item Binary conjunction: $n$ and $m$\\
			  Conjuncts two integers.\\
			  e.g. $7$ and $11 = 3$
		\item Binary disjunction: $n$ or $m$\\
			  Disjuncts two integers.\\
			  e.g. $7$ or $11 = 15$
		\item Binary contravalence: $n$ xor $m$\\
			  Contravalences two integers.\\
			  e.g. $7$ or $11 = 12$
		\item Greatest common divisor: $gcd(n; m)$\\
			  Computes the greatest common divisor of two integers.\\
			  e.g. $gcd(21; 28) = 7$
		\item Least common multiple: $lcm(n; m)$\\
			  Computes the least common multiple of two integers.\\
			  e.g. $lcm(3; 4) = 12$
		\item Sinus / Cosinus: $sin(x)$, $cos(x)$\\
			  Computes the sinus / cosinus of an angle.\\
			  Don't forget to specify the input unit (otherwise I'll use radians).\\
			  The output unit is always radian.\\
			  e.g. $sin(90 \deg) = \sin \frac{1}{4} \tau = 1$
		\item Conversions:
			  \begin{itemize}
			  	\item $rad(x\;$deg$)$: Degree $\Rightarrow$ Radians
			  	\item $rad(x\;$grad$)$: Gradian $\Rightarrow$ Radians
			  	\item $rad(x\;$turn$)$: $\tau$-Radians $\Rightarrow$ Radians
			  	\item $deg(x\;[$rad$])$: Radians $\Rightarrow$ Degree
			  	\item $deg(x\;$grad$)$: Gradian $\Rightarrow$ Degree
			  	\item $deg(x\;$turn$)$: $\tau$-Radians $\Rightarrow$ Degree
			  	\item $grad(x\;[$rad$])$: Radians $\Rightarrow$ Gradian
			  	\item $grad(x\;$deg$)$: Degree $\Rightarrow$ Gradian
			  	\item $grad(x\;$turn$)$: $\tau$-Radians $\Rightarrow$ Gradian
			  \end{itemize}
		\item Iterations: $iterate(firstx: expression)$\\
			  Runs the given iteration, resulting the fix point.\\
			  e.g. $iterate(4: (xn+(9/xn))/2) = iterate(4: \frac{x_n+{\frac{9}{x_n}}}{2}) = \sqrt{9} = 3$\\
			  expresses $x_{n+1} = \frac{x_n+{\frac{9}{x_n}}}{2}$
		\item Short sum: $sum(var: start < end \;[$\$$\; step]; expression)$\\
		      Sums the expression several times, iterating $var$ from $start$ to $end$.\\
		      e.g. $sum(i: 1 < 4; i) = \displaystyle\sum_{i=1}^{4} i = 1+2+3+4 = 10$
		\item Short product: $product(var: start < end \;[$\$$\; step]; expression)$\\
			  Multiplies the expression several times, iterating $var$ from $start$ to $end$.\\
			  e.g. $product(i: 1 < 5; i) = \displaystyle\prod_{i=1}^{5} i = 5! = 1\times2\times3\times4\times5 = 120$
		\item Zero: $zero(var: expr)$\\
			  Finds the zero of a function.\\
			  e.g. $zero(a: 5*a-55) = 11$\\
			  because $5\times11-55=0$
		\item Solve: $solve(var: expr1 = expr2)$\\
			  Solves the equation.\\
			  e.g. $solve(a: a\;\hat{}\;2=49) = 7$\\
			  because $7^2=49$
	\end{itemize}
	
	\subsection{Constants}
	
	Fu Bar knows these constants:
	
	\begin{itemize}
		\item tau: $\tau$, a full radian turn, about 6.28
		\item pi: $\pi$, $\frac{\tau}{2}$, a half radian turn, about 3.14
		\item phi: $\Phi$, the golden ratio, about 1.62
		\item full: A whole, 1
		\item half: $\frac{1}{2} = 0.5$
		\item quarter: $\frac{1}{4} = 0.25$
	\end{itemize}
	
	\subsection{Units}
	
	\begin{itemize}
		\item deg: Degrees, full turn = 360
		\item grad: Gradians, full turn = 400
		\item rad: Radians, full turn = $\tau$
		\item turn, tau: $\tau$-Radians, full turn = 1
		\item pi: $\pi$-Radians, full turn = 2
	\end{itemize}
	
	\subsection{Comparison}
	
	You can simply compare two expressions using an equation operator:\\
	$expression_1 = expression_2$\\
	\\
	Fu Bar will tell you the result, and whether the terms are equal or not.\\
	If not, it will tell you, which term is the greater one, and output the difference and the factor.
	
	\subsection{Custom variables}
	
	You can simply save results into your own variables:\\
	$[\,name\,]\;expression$\\
	\\
	Fu Bar will compute the term and save the result to a variable of your choice.\\
	To mark it as a constant, insert an exclamation mark before the name:\\
	$[\,!name\,]\;expression$\\\\
	Note: Fu Bar won't overwrite constants!
	
	\subsection{Custom functions}
	
	Of course, you can define custom functions, too:\\
	$[\,name(\,var\,)\,]\;expression$\\\\
	To mark it as read-only, insert an exclamation mark before the name:\\
	$[\,!name(\,var\,)\,]\;expression$\\\\
	To ensure, that the argument is not zero, add 'nonzero' before the var name:\\
	$[\,name(\,$nonzero$\,var\,)\,]\;expression$\\\\
	To assign a separate value to $name(0)$, enter:\\
	$[\,name(0)\,]\;expression$\\\\
	For example:\\
	\begin{tabular}{ll}
	$[\,f(x)\,]\;25x$ & $\Rightarrow 0$\\
    $f(4)$& $\Rightarrow 100$\\
    \\
    $[\,f($nonzero$\,x)\,]\;1/x$ & $\Rightarrow 1$\\
    $f(4)$ & $\Rightarrow 0.25$\\
    $f(0)$ & $\Rightarrow$ Function not defined for $x=0$\\
    \\
    $[\,f(0)\,]\;0$ & $\Rightarrow 0$\\
    $f(4)$ & $\Rightarrow 0.25$\\
    $f(0)$ & $\Rightarrow 0$
	\end{tabular}\\\\
	To ensure, that the argument is under a specific set of numbers,
	there are the following directives:\\
	\begin{description}
	  \item[complex] The full complex set.
	  \item[real] As a computer cannot calculate with irrational numbers,
	              $real$ equals $rational$.
	  \item[rational] The imaginary part is dropped, a rational number remains.
	  \item[integer] The fraction is truncated, an integer remains.
	  \item[natural] The sign is dropped, a natural number remains.
	\end{description}
	Each of these directives may be combined with $nonzero$.\\
	If no set is specified, Fu Bar uses $complex$.
	
	\subsection{Explanations}
	
	Fu Bar can tell you the steps, how to calculate a term.\\
	$:explain\;32*(1+5)$ will result:\\
	$1\,+\,5\,=\,6$\\
	$32\,*\,6\,=\,192$\\\\
	Come on, try it!
	
	\section{Plugins}
	
	Fu Bar provides a plugin interface. Plugins are invoked by one of these
	syntaxes:
	\begin{verbatim}
	:invoke plugin-name param-list
	/plugin-name param-list
	\end{verbatim}
	
	\subsection{Writing own plugins}
	
	Fu Bar wants its plugins to have the following exported procedures:
	\begin{description}
	  \item[void \_\_cdecl fubar\_plugin\_transmit(char *params)]
	    Receives the arguments. Do not implement the main skills here!
	    Always remember, that this procedure may be called multiple times
	    before invocation.
	  \item[void \_\_cdecl fubar\_plugin\_invoke()]
	    Implement all the plugin's functionality here.
	\end{description}
	
	A short example in Pascal:
	\begin{verbatim}
	library example;
	
	var params: string;
	
	procedure transmit(const s: PChar); cdecl;
	begin
	  params := params + ' ' + string(s);
	end;
	
	procedure invoke; cdecl;
	begin
	  Writeln('Hello World!');
	  Writeln(params);
	end;
	
	exports
	  transmit name 'fubar_plugin_transmit',
	  invoke name 'fubar_plugin_invoke';
	  
	initialization
	  params := '';
	end.
	\end{verbatim}
	
	Compile it, and you'll receive a file named \textit{libexample.so} (Unix) 
	or \textit{example.dll} (Windows).\\
	Now add your plugin to \textit{libplugs.dat}:
	\begin{verbatim}
	example: /etc/fubar/libexample.so
	\end{verbatim}
	If possible, the plugin should be in the global configuration path of Fu 
	Bar. On Linux, it's /etc/fubar/ in the most cases. Now don't forget to
	reinstall Fu Bar with the new \textit{libplugs.dat} (\texttt{sudo make 
	install}) and erase your local copy (usually in $\sim$/.config/fubar/)
	using \texttt{make erasecfg}.
	
	\subsection{tcal - the integrated task-based calendar}
	
	tcal is a task-based calendar, shipped as a plugin for fubar.
	To queue a task, use
	\begin{verbatim}
	/tcal queue task param-list
	/queue task param-list
	/task param-list
	\end{verbatim}
	
	For example, the \textit{dayofweek} task can be queued by
	\begin{verbatim}
	/tcal queue dayofweek 2011-11-11
	/queue dayofweek 2011-11-11
	/dayofweek 2011-11-11
	\end{verbatim}
	
	To run all queued tasks, enter
	\begin{verbatim}
	/tcal apply
	/apply
	\end{verbatim}
	
	\section{Get}
	
	\subsection{Using Git}
	
	Simply clone the repository:
	\begin{verbatim}
	git clone git://github.com/implementor/Fu-Bar.git fubar
	\end{verbatim}
	Later, you can easily check for updates:
	\begin{verbatim}
	cd fubar
	git pull origin master
	\end{verbatim}
	
	\subsection{Packed and compressed}
	
	Get it here: \url{https://github.com/implementor/Fu-Bar/zipball/master}
	
	\section{Build \& Install}
	
	On Linux, you can easily build Fu Bar using GNU \texttt{make}.
	Other Unixes may also work, but aren't tested.
	The packages \texttt{make} and \texttt{fpc} are required.
	
	\begin{description}
	  \item[make build] Build Fu Bar.
	  \item[make clean] Clean up the directory.
	  \item[make erasecfg] Erase your local configuration.
	  \item[sudo make install] Installs Fu Bar to \$(INST\_DEST)
	  \item[sudo make uninstall] Uninstall Fu bar from \$(INST\_DEST)
	  \item[make run] Run Fu Bar from the scratch.
	\end{description}
	
	If \texttt{wine} is available, and you have installed \texttt{FPC for
	Win32} using it, the following targets are also usable:
	
	\begin{description}
	  \item[make build4win] Build Fu Bar for Win32
	  \item[make buildX] Build Fu Bar for Win32 AND your current platform.
	  \item[make run4win] Run the Win32 executable
	\end{description}
	
	\section{Run}
	
	After installation, you should be able to call \texttt{fubar} from
	the command-line.\\
	\texttt{fubar --help} reveals this:
	
	\begin{verbatim}
	Fu Bar, a term-parsing calculator.
	Copyright (c) 2011 Marvin Cohrs
	Distributed under the terms of the GNU General Public License.

	Usage: fubar [-i|--instant] [-q|--quiet] [--noman] [[-t|--term] TERM]
       fubar --safe [[-t|--term] TERM]
       fubar --about TOPIC
       fubar --help

	  -i --instant      Do not load my ~/.config/fubar/autoload
	  -q --quiet        Be quiet.
	  -t --term TERM    Calculate the given term.
	     --noman        Disable built-in manual.
	     --safe         Safe mode, does not read or modify any file.
	     --help         This help screen.
	     --about TOPIC  Displays help about a specific topic.
     
	--term implies --quiet
	--safe implies --quiet, --instant, --noman
	--help, --about deny --safe, --noman
	\end{verbatim}
	
	Fu Bar also provides a manpage. Try \texttt{man fubar} ;)

\end{document}